---
title: "epi570-model-testing"
output: pdf_document
date: "`r Sys.Date()`"
---
setting up / loading packages
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

pacman::p_load(pacman, EpiModel, ggplot2, tidyverse, reshape2)
```

**PENDING THOUGHTS**
Can't get the combined vaccine scenario to work. Thinking about scraping that, also in the interest of time.

build model foundation:
    - conceptualized as relatively low baseline vaccination rate with 9vHPV vaccine
    - vaccine assumed to have immunogenecity (~97% produce sufficient response)
    - vaccinated people assumed to become infected through vaccine leak (~90% efficacy)
    - vaccine assumed to act through prevention of infection in vaccinated people (lower FOI) 
```{r Vaccination Model}
Vaccination <- function(t, t0, parms) {
  with(as.list(c(t0, parms)), {
    
#1. Track Population Sizes ###############################################################
    # total male population size
    m.num = uv.m.ue.num + uv.m.e.num + uv.m.i.a.num + uv.m.i.s.num + 
            v.m.ue.num  + v.m.e.num  + v.m.i.a.num  + v.m.i.s.num

    # total female population size
    f.num = uv.f.ue.num + uv.f.e.num + uv.f.i.a.num + uv.f.i.s.num + 
            v.f.ue.num  + v.f.e.num  + v.f.i.a.num  + v.f.i.s.num

    # total population
    num = f.num + m.num

    # infected numbers for contact proportions
    i.m.num = uv.m.i.a.num + uv.m.i.s.num + v.m.i.a.num  + v.m.i.s.num   # males
    i.f.num = uv.f.i.a.num + uv.f.i.s.num + v.f.i.a.num  + v.f.i.s.num   # females
  
    
#2. Define Contact Rate ##################################################################
    # contact rate for females dependent on contact rate for males
    # forcing dissortative heterosexual contact only
    ce.f <- (ce.m * m.num) / f.num


#3. Define Lambda ########################################################################
    # conceptualizing 9vHPV Gardasil vaccine as reducing likelihood of becoming infected 
    # with HPV due to high efficacy (psi). thus, dynamics of HPV itself are same between
    # susceptible & vaccinated, but the vaccinated FOI is reduced by the complement of vaccine
    # efficacy (1-psi)
    
    ### EXTERNAL FOI ADD?
    
  # susceptibles
    # males
    #lambda.m.s.ex <- (tau) * (ce.m) * (i.f.prev) 
    lambda.m.s <- (tau) * (ce.m) * (i.f.num / f.num)
    #lambda.m.s <- lambda.m.s.ex + lambda.m.s.in
    # females
    #lambda.f.s.ex <-  (tau) * (ce.f) * (i.m.prev)
    lambda.f.s <-  (tau) * (ce.f) * (i.m.num / m.num)
    #lambda.f.s <- lambda.f.s.ex + lambda.f.s.in
    # This is a constant while the force of infection wont change based on the changing prevalence in males. How can we include the population prevalence and population specific prevalence
  
  # vaccinated
    # males
    lambda.m.v <- (tau)*(1-psi) * (ce.m)*(i.f.num / f.num)
    #lambda.m.v <- (tau)*(1-psi) * (ce.m)*(i.f.prev) 
    # females
    lambda.f.v <-  (tau)*(1-psi) * (ce.f)*(i.m.num / m.num)
    #lambda.f.v <-  (tau)*(1-psi) * (ce.f)*(i.m.prev)


#4. Define Additional parameters #########################################################
  # recovery rate: 1/duration of infection, allowing for differential clearing rate by vax status & symptomatic status 
    # susceptible recovery rate
      delta.s.a <- 1/dur.inf.s.a
      delta.s.s <- 1/dur.inf.s.s
    # vaccinated recovery rate
      delta.v.a <- 1/dur.inf.v.a
      delta.v.s <- 1/dur.inf.v.s
    
    # zeta is the proportion of susceptibles that become symptomatic 
    # kappa is the proportion of susceptible exposed that become vaccinated exposed at each timestep
    # nu is birthrate

#5. Define Differential Equations ########################################################
  
# MALES : SUSCEPTIBLE
  # susceptible unexposed (11-18 yrs old) [uv.m.ue.num]
  dS.m.ue <- ((0.5 * (1-omega.m*chi) * nu*num)) +            # births
             (-age.in * uv.m.ue.num) + (-mu.ue * uv.m.ue.num)  # gen pop
      # entry multiplied by half to account for M/F strata
      # S populated by complement of proportion vaccinated*proportion immunologic

  # susceptible exposed (18+, proxy for sexually active) [uv.m.e.num]
  dS.m.e <- (age.in * uv.m.ue.num) + (-mu * uv.m.e.num) + (-age.out * uv.m.e.num) +         # general pop
            (-lambda.m.s * zeta.s * uv.m.e.num) + (-lambda.m.s * (1-zeta.s) * uv.m.e.num) + # exposure
            (delta.s.a * uv.m.i.a.num) + (delta.s.s * uv.m.i.s.num) +                       # recovery
            (-kappa * uv.m.e.num)                                                         # catch-up vax
  
 # infected asymptomatic [uv.m.i.a.num]
  dI.m.s.a <- (-age.out * uv.m.i.a.num) + (-mu * uv.m.i.a.num) +  # general pop
              (lambda.m.s * (1-zeta.s) * uv.m.e.num) +           # asymptomatic infection
              (-delta.s.a * uv.m.i.a.num)                         # recovery
    
  # infected symptomatic [uv.m.i.s.num]
  dI.m.s.s <- (lambda.m.s * zeta.s * uv.m.e.num) +               # symptomatic infection
              (-delta.s.s * uv.m.i.s.num) +                        # recovery
              (-age.out * uv.m.i.s.num) + (-mu * uv.m.i.s.num)       # general pop


# MALES : VACCINATED
  # vaccinated unexposed [v.m.ue.num]
  dV.m.ue <- (0.5 * omega.m * chi * nu * num) +              # births
             (-age.in * v.m.ue.num) + (-mu.ue * v.m.ue.num)  # general pop

  # vaccinated exposed/sexually active [v.m.e.num]
  dV.m.e <- (age.in * v.m.ue.num) + (-age.out * v.m.e.num) + (-mu * v.m.e.num) +         # general pop
            (-lambda.m.v * (zeta.v) * v.m.e.num) + (-lambda.m.v * (1- zeta.v) * v.m.e.num) + # exposure
            (delta.v.a * v.m.i.a.num) + (delta.v.s * v.m.i.s.num) +                      # recovery
            (kappa * uv.m.e.num)                                                       # catch-up vax

  # infected asymptomatic [v.m.i.a.num]
  dI.m.v.a <- (-age.out * v.m.i.a.num) + (-mu * v.m.i.a.num) +        # gen pop
              (lambda.m.v * (1- zeta.v) * v.m.e.num) +                 # asymptomatic infection
              (-delta.v.a * v.m.i.a.num)                              # recovery
  # infected symptomatic [v.m.i.s.num]
  dI.m.v.s <- (-age.out * v.m.i.s.num) + (-mu * v.m.i.s.num) +        # gen pop
              (lambda.m.v * (zeta.v) * v.m.e.num) +                    # symptomatic infection
              (-delta.v.s * v.m.i.s.num)                              # recovery  

  
# FEMALES : SUSCEPTIBLE
  # unexposed [uv.f.ue.num]
  dS.f.ue <- ((0.5 * (1-omega.f*chi) * nu * num)) - (age.in * uv.f.ue.num) - (mu.ue * uv.f.ue.num)
  
  # exposed/sexually active [uv.f.e.num]
  dS.f.e <- (age.in * uv.f.ue.num) + (-mu * uv.f.e.num) + (-age.out * uv.f.e.num) +       # general pop
            (-lambda.f.s * zeta.s * uv.f.e.num) + (-lambda.f.s * (1-zeta.s) * uv.f.e.num) +   # exposure
            (delta.s.a * uv.f.i.a.num) + (delta.s.s * uv.f.i.s.num) +                     # recovery
            (-kappa * uv.f.e.num)                                                       # catch-up vax
  
  # infected, asymptomatic [uv.f.i.a.num]
  dI.f.s.a <- (-age.out * uv.f.i.a.num) + (-mu * uv.f.i.a.num) +  # general pop
              (lambda.f.s * (1-zeta.s) * uv.f.e.num) +              # asymptomatic infection
              (-delta.s.a * uv.f.i.a.num)                         # recovery
    
  # infected, symptomatic [uv.f.i.s.num]
  dI.f.s.s <- (lambda.f.s * zeta.s * uv.f.e.num) +                     # symptomatic infection
              (-delta.s.s * uv.f.i.s.num) +                          # recovery
              (-age.out * uv.f.i.s.num) + (-mu * uv.f.i.s.num)       # general pop

  
# FEMALES : VACCINATED
  # unexposed [v.f.ue.num]
  dV.f.ue <- (0.5 * omega.f * chi * nu * num) +              # births
             (-age.in * v.f.ue.num) + (-mu.ue * v.f.ue.num)  # general pop
  # exposed [v.f.e.num]
  dV.f.e <- (age.in * v.f.ue.num) + (-age.out * v.f.e.num) + (-mu * v.f.e.num) +       # gen pop
            (-lambda.f.v * zeta.v * v.f.e.num) + (-lambda.f.v * (1-zeta.v) * v.f.e.num) +  # infection
            (delta.v.a * v.f.i.a.num) + (delta.v.s * v.f.i.s.num) +                    # recovery
            (kappa * uv.f.e.num)                                                       # catch-up vax

  # infected, asymptomatic [v.f.i.a.num]
  dI.f.v.a <- (-age.out * v.f.i.a.num) + (-mu * v.f.i.a.num) +        # gen pop
              (lambda.f.v * (1-zeta.v) * v.f.e.num) +                   # asymptomatic infection
              (-delta.v.a * v.f.i.a.num)                              # recovery
  # infected, symptomatic [v.f.i.s.num]
  dI.f.v.s <- (-age.out * v.f.i.s.num) + (-mu * v.f.i.s.num) +        # gen pop
              (lambda.f.v * zeta.v * v.f.e.num) +                       # symptomatic infection
              (-delta.v.s * v.f.i.s.num)                              # recovery  

  
  
# 6.Outputs ##############################################################################
list(c(dS.m.ue, dS.m.e, dI.m.s.a, dI.m.s.s, 
       dV.m.ue, dV.m.e, dI.m.v.a, dI.m.v.s,
       dS.f.ue, dS.f.e, dI.f.s.a, dI.f.s.s, 
       dV.f.ue, dV.f.e, dI.f.v.a, dI.f.v.s,
       si.m.flow = (lambda.m.s * uv.m.e.num),
       vi.m.flow = (lambda.m.v * v.m.e.num),
       sv.m.flow = (kappa * uv.m.e.num),
       si.f.flow = (lambda.f.s * uv.f.e.num),
       vi.f.flow = (lambda.f.v * v.f.e.num),
       sv.f.flow = (kappa * uv.f.e.num))
       )
  })
}

```


```{r Omega.f Vaccination}
# Vaccination Scenario 1.) Male vaccination at birth increased from 0.1 to 0.8 by 0.2       
param <- param.dcm( # FOI parameters
                    tau = 0.60, psi = 0.90, 
                    # contact parameter : changing this because we have a per-act tau (not per-partner)
                    # ce.m = (5/365),
# ce.m = (per-act transmission prob)(avg # sex acts per partner)(avg # diff partners per year)
# (1.5)(16)
                    ce.m = (30/365),
                    # general pop parameters
                    i.f.prev = 0.4, # US population prevalence of HPV amoung women
                    i.m.prev = 0.4, # US population prevalence of HPV amoung men
                    nu = (((20)/1000)/365), # this rate is the whole US, not age-group specific - needs fixing
                    mu.ue = (50/1e5)/365, mu = (100/1e5)/365, # these rates are estimated for teens & young adults, respectively
                    age.in = (1/(7*365)), age.out = (1/(47*365)),
                    # recovery parameters
                        # assumed duration symptomatic is sub-component of total time infected
                    dur.inf.s.a = (1.5*365), dur.inf.s.s= (1.25*365),
                    dur.inf.v.a = (1.25*365), dur.inf.v.s = (1*365),
                    # vaccine parameters
                    omega.m = c(0.1,0.2,0.3,0.4), omega.f = 0.40, 
                    chi = 0.97, kappa = (0.0025/365),
                    # symptomatic parameters
                    # zeta is the proportion of susceptible that become symptomatic
                    zeta.v = (0.2) , zeta.s = (0.2))


init <- init.dcm( # males
                 uv.m.ue.num = 1.6e6, uv.m.e.num = 8.2e6,
                 uv.m.i.a.num = 2.8e5, uv.m.i.s.num= 2.5e6,
                 v.m.ue.num = 3.04e5, v.m.e.num = 1e7, 
                 v.m.i.a.num = 3.2e6, v.m.i.s.num = 3.6e5,
                 # females
                 uv.f.ue.num = 1.7e6, uv.f.e.num = 5.8e6, 
                 uv.f.i.a.num = 3.5e6, uv.f.i.s.num = 3.7e5,
                 v.f.ue.num = 2.4e5, v.f.e.num = 3.2e6, 
                 v.f.i.a.num = 9e6, v.f.i.s.num = 1e6,
                 # flows
                 si.m.flow = 0, vi.m.flow = 0, sv.m.flow = 0,
                 si.f.flow = 0, vi.f.flow = 0, sv.f.flow = 0)



control <- control.dcm(nsteps = (50*365), new.mod = Vaccination)

mod <- dcm(param, init, control)
mod
```


```{r Kappa Vaccination}
# Vaccination Scenario 2.) Catch-up Vaccination increased from 0.01 to 0.04
param2 <- param.dcm( # FOI parameters
                    tau = 0.60, psi = 0.90, 
                    # contact parameter : changing this because we have a per-act tau (not per-partner)
                    # ce.m = (5/365),
# ce.m = (per-act transmission prob)(avg # sex acts per partner)(avg # diff partners per year)
# (1.5)(16)
                    ce.m = (30/365),
                    # general pop parameters
                    i.f.prev = 0.4, # US population prevalence of HPV amoung women
                    i.m.prev = 0.4, # US population prevalence of HPV amoung men
                    nu = (((20)/1000)/365), # this rate is the whole US, not age-group specific - needs fixing
                    mu.ue = (50/1e5)/365, mu = (100/1e5)/365, # these rates are estimated for teens & young adults, respectively
                    age.in = (1/(7*365)), age.out = (1/(47*365)),
                    # recovery parameters
                        # assumed duration symptomatic is sub-component of total time infected
                    dur.inf.s.a = (1.5*365), dur.inf.s.s= (1.25*365),
                    dur.inf.v.a = (1.25*365), dur.inf.v.s = (1*365),
                    # vaccine parameters
                    omega.m = 0.10, omega.f = 0.40, 
                    chi = 0.97, kappa = (seq((0.01/365), (0.1/365), by = (0.01/265))),
                    # symptomatic parameters
                    # zeta is the proportion of susceptible that become symptomatic
                    zeta.v = (0.2) , zeta.s = (0.2))

mod2 <- dcm(param2, init, control)
mod2
```
```{r Omega.f Vaccination}
# Vaccination Scenario 3.) Combine previous scenarios
param3 <- param.dcm( # FOI parameters
                    tau = 0.60, psi = 0.90, 
                    # contact parameter : changing this because we have a per-act tau (not per-partner)
                    # ce.m = (5/365),
# ce.m = (per-act transmission prob)(avg # sex acts per partner)(avg # diff partners per year)
# (1.5)(16)
                    ce.m = (30/365),
                    # general pop parameters
                    i.f.prev = 0.4, # US population prevalence of HPV amoung women
                    i.m.prev = 0.4, # US population prevalence of HPV amoung men
                    nu = (((20)/1000)/365), # this rate is the whole US, not age-group specific - needs fixing
                    mu.ue = (50/1e5)/365, mu = (100/1e5)/365, # these rates are estimated for teens & young adults, respectively
                    age.in = (1/(7*365)), age.out = (1/(47*365)),
                    # recovery parameters
                        # assumed duration symptomatic is sub-component of total time infected
                    dur.inf.s.a = (1.5*365), dur.inf.s.s= (1.25*365),
                    dur.inf.v.a = (1.25*365), dur.inf.v.s = (1*365),
                    # vaccine parameters
                    omega.m = 0.1, omega.f = c(0.30, 0.40, 0.50, 0.60), 
                    chi = 0.97, kappa = (0.01/365),
                    # symptomatic parameters
                    # zeta is the proportion of susceptible that become symptomatic
                    zeta.v = (0.2) , zeta.s = (0.2))

mod3 <- dcm(param3, init, control)
mod3
```


Plotting Omega Vaccine Scenario
```{r Vaccination Scenario 1}
mod <- mutate_epi(mod, m.num = uv.m.ue.num + uv.m.e.num + uv.m.i.a.num + uv.m.i.s.num + 
                               v.m.ue.num  + v.m.e.num  + v.m.i.a.num  + v.m.i.s.num)

mod <- mutate_epi(mod, f.num = uv.f.ue.num + uv.f.e.num + uv.f.i.a.num + uv.f.i.s.num + 
                               v.f.ue.num  + v.f.e.num  + v.f.i.a.num  + v.f.i.s.num)

mod <- mutate_epi(mod, i.m.num = uv.m.i.a.num + uv.m.i.s.num + v.m.i.a.num  + v.m.i.s.num)
mod <- mutate_epi(mod, i.f.num = uv.f.i.a.num + uv.f.i.s.num + v.f.i.a.num  + v.f.i.s.num)

mod <- mutate_epi(mod, m.prev = i.m.num / m.num)
mod <- mutate_epi(mod, f.prev = i.f.num / f.num)
```

males: 
```{r}
par(mfrow = c(1,1))
plot(mod, y = c("uv.m.ue.num", 'uv.m.e.num', 'uv.m.i.a.num', 'uv.m.i.s.num'),
                legend='full')
```

```{r}
par(mfrow = c(1,1))
plot(mod, y = c("v.m.ue.num", 'v.m.e.num', 'v.m.i.a.num', 'v.m.i.s.num'),
                legend='full', run=1)
```


```{r}
par(mfrow = c(1,2))
plot(mod, y = "m.prev", main = "Proportional Prevalence for Males")
plot(mod, y = "f.prev", main = "Proportional Prevalence for Females")
legend("bottomright", legend = c("omega.m = 0.1", "omega.m = 0.3","omega.m = 0.5", "omega.m = 0.7"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r}
par(mfrow = c(1,2))
plot(mod, y = "i.m.num", main = "Prevalence for Males")
plot(mod, y = "i.f.num", main = "Prevalence for Females")

par(mfrow = c(1,2))
plot(mod, y = "m.num", main = "Population Size (Males)")
plot(mod, y = "f.num", main = "Population Size (Females)")

```

```{r}
par(mfrow = c(1,2))
plot(mod, y = "si.m.flow", main = "si.Males")
plot(mod, y = "si.f.flow", main = "si.Females")
legend("bottomright", legend = c("omega.m = 0.1", "omega.m = 0.3","omega.m = 0.5", "omega.m = 0.7"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r}
par(mfrow = c(1,2))
plot(mod, y = "vi.m.flow", main = "vi.Males", legend='full')
plot(mod, y = "vi.f.flow", main = "vi.Females", legend='full')
legend("bottomright", legend = c("omega.m = 0.1", "omega.m = 0.3","omega.m = 0.5", "omega.m = 0.7"), col = c("red", "blue", "green", "purple"), pch = 19)
```
Plotting Kappa Vaccine Scenario
```{r Vaccination Scenario 2}
mod2 <- mutate_epi(mod2, m.num = uv.m.ue.num + uv.m.e.num + uv.m.i.a.num + uv.m.i.s.num + 
                               v.m.ue.num  + v.m.e.num  + v.m.i.a.num  + v.m.i.s.num)

mod2 <- mutate_epi(mod2, f.num = uv.f.ue.num + uv.f.e.num + uv.f.i.a.num + uv.f.i.s.num + 
                               v.f.ue.num  + v.f.e.num  + v.f.i.a.num  + v.f.i.s.num)

mod2 <- mutate_epi(mod2, i.m.num = uv.m.i.a.num + uv.m.i.s.num + v.m.i.a.num  + v.m.i.s.num)
mod2 <- mutate_epi(mod2, i.f.num = uv.f.i.a.num + uv.f.i.s.num + v.f.i.a.num  + v.f.i.s.num)

mod2 <- mutate_epi(mod2, m.prev = i.m.num / m.num)
mod2 <- mutate_epi(mod2, f.prev = i.f.num / f.num)

data <- as.data.frame(mod2)

data02 <- as.data.frame(mod2, run=1)
```

males: 
```{r}
par(mfrow = c(1,1))
plot(mod2, y = c("uv.m.ue.num", 'uv.m.e.num', 'uv.m.i.a.num', 'uv.m.i.s.num'),
                legend='full')
```

```{r}
par(mfrow = c(1,1))
plot(mod2, y = c("v.m.ue.num", 'v.m.e.num', 'v.m.i.a.num', 'v.m.i.s.num'),
                legend='full', run=1)
```


```{r}
par(mfrow = c(1,2))
plot(mod2, y = "m.prev", main = "Proportional Prevalence for Males")
plot(mod2, y = "f.prev", main = "Proportional Prevalence for Females")
legend("bottomright", legend = c("kappa = 0.01", "kappa = 0.02","kappa = 0.03", "kappa = 0.04"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r}
par(mfrow = c(1,2))
plot(mod2, y = "i.m.num", main = "Prevalence for Males")
plot(mod2, y = "i.f.num", main = "Prevalence for Females")

par(mfrow = c(1,2))
plot(mod2, y = "m.num", main = "Population Size (Males)")
plot(mod2, y = "f.num", main = "Population Size (Females)")

```

```{r}
par(mfrow = c(1,2))
plot(mod2, y = "si.m.flow", main = "si.Males")
plot(mod2, y = "si.f.flow", main = "si.Females")
legend("bottomright", legend = c("kappa = 0.01", "kappa = 0.02","kappa = 0.03", "kappa = 0.04"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r}
par(mfrow = c(1,2))
plot(mod2, y = "vi.m.flow", main = "vi.Males", legend='full')
plot(mod2, y = "vi.f.flow", main = "vi.Females", legend='full')
legend("bottomright", legend = c("kappa = 0.01", "kappa = 0.02","kappa = 0.03", "kappa = 0.04"), col = c("red", "blue", "green", "purple"), pch = 19)
```



Plotting Omega + Kappa Vaccine Scenario
```{r Vaccination Scenario 2}
mod3 <- mutate_epi(mod3, m.num = uv.m.ue.num + uv.m.e.num + uv.m.i.a.num + uv.m.i.s.num + 
                               v.m.ue.num  + v.m.e.num  + v.m.i.a.num  + v.m.i.s.num)

mod3 <- mutate_epi(mod3, f.num = uv.f.ue.num + uv.f.e.num + uv.f.i.a.num + uv.f.i.s.num + 
                               v.f.ue.num  + v.f.e.num  + v.f.i.a.num  + v.f.i.s.num)

mod3 <- mutate_epi(mod3, i.m.num = uv.m.i.a.num + uv.m.i.s.num + v.m.i.a.num  + v.m.i.s.num)
mod3 <- mutate_epi(mod3, i.f.num = uv.f.i.a.num + uv.f.i.s.num + v.f.i.a.num  + v.f.i.s.num)

mod3 <- mutate_epi(mod3, m.prev = i.m.num / m.num)
mod3 <- mutate_epi(mod3, f.prev = i.f.num / f.num)

data <- as.data.frame(mod3)

data03 <- as.data.frame(mod3, run=1)
```

males: 
```{r}
par(mfrow = c(1,1))
plot(mod3, y = c("uv.m.ue.num", 'uv.m.e.num', 'uv.m.i.a.num', 'uv.m.i.s.num'),
                legend='full')
```

```{r}
par(mfrow = c(1,1))
plot(mod3, y = c("v.m.ue.num", 'v.m.e.num', 'v.m.i.a.num', 'v.m.i.s.num'),
                legend='full', run=1)
```


```{r}
par(mfrow = c(1,2))
plot(mod3, y = "m.prev", main = "Proportional Prevalence for Males")
plot(mod3, y = "f.prev", main = "Proportional Prevalence for Females")
legend("bottomright", legend = c("omega.m = 0.1 + kappa = 0.01", "omega.m = 0.3 + kappa = 0.02","omega.m = 0.5 + kappa = 0.03", "omega.m = 0.7 + kappa = 0.04"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r}
par(mfrow = c(1,2))
plot(mod3, y = "i.m.num", main = "Prevalence for Males")
plot(mod3, y = "i.f.num", main = "Prevalence for Females")

par(mfrow = c(1,2))
plot(mod3, y = "m.num", main = "Population Size (Males)")
plot(mod3, y = "f.num", main = "Population Size (Females)")

```

```{r}
par(mfrow = c(1,2))
plot(mod3, y = "si.m.flow", main = "si.Males")
plot(mod3, y = "si.f.flow", main = "si.Females")
legend("bottomright", legend = c("omega.m = 0.1 + kappa = 0.01", "omega.m = 0.3 + kappa = 0.02","omega.m = 0.5 + kappa = 0.03", "omega.m = 0.7 + kappa = 0.04"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r}
par(mfrow = c(1,2))
plot(mod3, y = "vi.m.flow", main = "vi.Males", legend='full')
plot(mod3, y = "vi.f.flow", main = "vi.Females", legend='full')
legend("bottomright", legend = c("omega.m = 0.1 + kappa = 0.01", "omega.m = 0.3 + kappa = 0.02","omega.m = 0.5 + kappa = 0.03", "omega.m = 0.7 + kappa = 0.04"), col = c("red", "blue", "green", "purple"), pch = 19)
```

```{r Vaccine Impact analysis Failed Function}
# simulation <- c("mod")
# 
# effects <- function(X){
#     df<-as.data.frame(X, run = 1)
#     df2<-as.data.frame(X, run = 2)
#     df3<-as.data.frame(X, run = 3)
#     df4<-as.data.frame(X, run = 4)
#   
#     # Calculate metrics
#     metrics <- list(
#         # Number of Infections Averted in Females
#         NIA_females = c(
#             sum(df$si.f.flow)-sum(df2$si.f.flow),
#             sum(df$si.f.flow)-sum(df3$si.f.flow),
#             sum(df$si.f.flow)-sum(df4$si.f.flow)
#         ),
#       
#         # Percent Infections Averted in Females
#         percent_averted_females = c(
#             (sum(df$si.f.flow)-sum(df2$si.f.flow))/sum(df$si.f.flow),
#             (sum(df$si.f.flow)-sum(df3$si.f.flow))/sum(df$si.f.flow),
#             (sum(df$si.f.flow)-sum(df4$si.f.flow))/sum(df$si.f.flow)
#         ),
#       
#         # Number Needed to Treat for Females 
#         NNT_females = c(
#             sum(df2$v.m.ue.num)/(sum(df$si.f.flow)-sum(df2$si.f.flow)),
#             sum(df3$v.m.ue.num)/(sum(df$si.f.flow)-sum(df3$si.f.flow)),
#             sum(df4$v.m.ue.num)/(sum(df$si.f.flow)-sum(df4$si.f.flow))
#         ),
#       
#         # Number of Infections Averted in Males
#         NIA_males = c(
#             sum(df$si.m.flow)-sum(df2$si.m.flow),
#             sum(df$si.m.flow)-sum(df3$si.m.flow),
#             sum(df$si.m.flow)-sum(df4$si.m.flow)
#         ),
#       
#         # Percent of Infections Averted in Males
#         percent_averted_males = c(
#             (sum(df$si.m.flow)-sum(df2$si.m.flow))/sum(df$si.m.flow),
#             (sum(df$si.m.flow)-sum(df3$si.m.flow))/sum(df$si.m.flow),
#             (sum(df$si.m.flow)-sum(df4$si.m.flow))/sum(df$si.m.flow)
#         ),
#       
#         # Number Needed to Treat in Males
#         NNT_males = c(
#             sum(df2$v.m.ue.num)/(sum(df$si.m.flow)-sum(df2$si.m.flow)),
#             sum(df3$v.m.ue.num)/(sum(df$si.m.flow)-sum(df3$si.m.flow)),
#             sum(df4$v.m.ue.num)/(sum(df$si.m.flow)-sum(df4$si.m.flow))
#         )
#     )
#   
#     return(metrics)
# }
# 
# results <- lapply(simulation, effects)


```



```{r Omega.m Vaccinatinon}
#Direct and Indirect Effects graphed.
# 11-17 Male vax scenario outcomes
df<-as.data.frame(mod, run = 1)
df2<-as.data.frame(mod, run = 2)
df3<-as.data.frame(mod, run = 3)
df4<-as.data.frame(mod, run = 4)

#Number of Infections Averted in Females
NIA1<-sum(df$si.f.flow)-sum(df2$si.f.flow)
NIA1

NIA2<-sum(df$si.f.flow)-sum(df3$si.f.flow)
NIA2


NIA3<-sum(df$si.f.flow)-sum(df4$si.f.flow)
NIA3
#Percent Infections Averted in Females
NIA1/sum(df$si.f.flow)
NIA2/sum(df$si.f.flow)
NIA3/sum(df$si.f.flow)

#Number Needed to Treat for Females 
sum(df2$v.m.ue.num)/NIA1
sum(df3$v.m.ue.num)/NIA2
sum(df4$v.m.ue.num)/NIA3

#(sum(df2$v.m.ue.num)+sum(df2$v.m.e.num)+sum(df2$v.m.i.a.num)+sum(df2$v.m.i.s.num))/NIA1
#(sum(df3$v.m.ue.num)+sum(df3$v.m.e.num)+sum(df3$v.m.i.a.num)+sum(df3$v.m.i.s.num))/NIA2             
#(sum(df4$v.m.ue.num)+sum(df4$v.m.e.num)+sum(df4$v.m.i.a.num)+sum(df4$v.m.i.s.num))/NIA3



#Number of Infections Averted in Males
NIA4<-sum(df$si.m.flow)-sum(df2$si.m.flow)
NIA4

NIA5<-sum(df$si.m.flow)-sum(df3$si.m.flow)
NIA5


NIA6<-sum(df$si.m.flow)-sum(df4$si.m.flow)
NIA6

#Percent of Infections Averted in Males
NIA4/sum(df$si.m.flow)
NIA5/sum(df$si.m.flow)
NIA6/sum(df$si.m.flow)

#Number Needed to Treat in Males
sum(df2$v.m.ue.num)/NIA4
sum(df3$v.m.ue.num)/NIA5
sum(df4$v.m.ue.num)/NIA6
```
```{r Kappa Vaccination}
#Direct and Indirect Effects graphed.
# 11-17 Male vax scenario outcomes
df<-as.data.frame(mod2,  run = 1)
df2<-as.data.frame(mod2, run = 2)
df3<-as.data.frame(mod2, run = 3)
df4<-as.data.frame(mod2, run = 4)

#Number of Infections Averted in Females
NIA1<-sum(df$si.f.flow)-sum(df2$si.f.flow)
NIA1

NIA2<-sum(df$si.f.flow)-sum(df3$si.f.flow)
NIA2


NIA3<-sum(df$si.f.flow)-sum(df4$si.f.flow)
NIA3
#Percent Infections Averted in Females
NIA1/sum(df$si.f.flow)
NIA2/sum(df$si.f.flow)
NIA3/sum(df$si.f.flow)

#Number Needed to Treat for Females 
sum(df2$v.m.ue.num)/NIA1
sum(df3$v.m.ue.num)/NIA2
sum(df4$v.m.ue.num)/NIA3

#(sum(df2$v.m.ue.num)+sum(df2$v.m.e.num)+sum(df2$v.m.i.a.num)+sum(df2$v.m.i.s.num))/NIA1
#(sum(df3$v.m.ue.num)+sum(df3$v.m.e.num)+sum(df3$v.m.i.a.num)+sum(df3$v.m.i.s.num))/NIA2             
#(sum(df4$v.m.ue.num)+sum(df4$v.m.e.num)+sum(df4$v.m.i.a.num)+sum(df4$v.m.i.s.num))/NIA3



#Number of Infections Averted in Males
NIA4<-sum(df$si.m.flow)-sum(df2$si.m.flow)
NIA4

NIA5<-sum(df$si.m.flow)-sum(df3$si.m.flow)
NIA5


NIA6<-sum(df$si.m.flow)-sum(df4$si.m.flow)
NIA6

#Percent of Infections Averted in Males
NIA4/sum(df$si.m.flow)
NIA5/sum(df$si.m.flow)
NIA6/sum(df$si.m.flow)

#Number Needed to Treat in Males
sum(df2$v.m.ue.num)/NIA4
sum(df3$v.m.ue.num)/NIA5
sum(df4$v.m.ue.num)/NIA6
```
```{r Omega.f Vaccinatinon}
#Direct and Indirect Effects graphed.
# 11-17 Male vax scenario outcomes
df<-as.data.frame(mod3, run = 1)
df2<-as.data.frame(mod3, run = 2)
df3<-as.data.frame(mod3, run = 3)
df4<-as.data.frame(mod3, run = 4)

#Number of Infections Averted in Females
NIA1<-sum(df$si.f.flow)-sum(df2$si.f.flow)
NIA1

NIA2<-sum(df$si.f.flow)-sum(df3$si.f.flow)
NIA2


NIA3<-sum(df$si.f.flow)-sum(df4$si.f.flow)
NIA3
#Percent Infections Averted in Females
NIA1/sum(df$si.f.flow)
NIA2/sum(df$si.f.flow)
NIA3/sum(df$si.f.flow)

#Number Needed to Treat for Females 
sum(df2$v.m.ue.num)/NIA1
sum(df3$v.m.ue.num)/NIA2
sum(df4$v.m.ue.num)/NIA3

#(sum(df2$v.m.ue.num)+sum(df2$v.m.e.num)+sum(df2$v.m.i.a.num)+sum(df2$v.m.i.s.num))/NIA1
#(sum(df3$v.m.ue.num)+sum(df3$v.m.e.num)+sum(df3$v.m.i.a.num)+sum(df3$v.m.i.s.num))/NIA2             
#(sum(df4$v.m.ue.num)+sum(df4$v.m.e.num)+sum(df4$v.m.i.a.num)+sum(df4$v.m.i.s.num))/NIA3



#Number of Infections Averted in Males
NIA4<-sum(df$si.m.flow)-sum(df2$si.m.flow)
NIA4

NIA5<-sum(df$si.m.flow)-sum(df3$si.m.flow)
NIA5


NIA6<-sum(df$si.m.flow)-sum(df4$si.m.flow)
NIA6

#Percent of Infections Averted in Males
NIA4/sum(df$si.m.flow)
NIA5/sum(df$si.m.flow)
NIA6/sum(df$si.m.flow)

#Number Needed to Treat in Males
sum(df2$v.m.ue.num)/NIA4
sum(df3$v.m.ue.num)/NIA5
sum(df4$v.m.ue.num)/NIA6
```



